%!TEX program = xelatex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Manuel}{Pineyro}{ Full stack developer with a diverse skill set encompassing marketing, design, and development. \\ \vspace{\topsep} \href{mailto:manuel.o.pineyro@gmail.com}{manuel.o.pineyro@gmail.com} | 914.564.5325
}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Columbia University}
\descript{Major: Psychology \\ Minor: Business Management}
\location{Graduation May 2012 | New York, NY}
Dean's List
\sectionsep

\subsection{NYU}
\descript{Interactive Telecommunications Program Camp 2012}
\location{Completed July 2012 | New York, NY}
Physical Computing | UX | Interactive Media
\sectionsep

\subsection{Epicodus}
\descript{Web Development Bootcamp}
\location{Graduation June 2014 | Portland, OR}
Ruby | JavaScript | HTML | CSS
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Media \& Information Management \\
\sectionsep

\subsection{Undergraduate}
Business of Software Development \\
Intro to Computer Science \\
Adv Computer Modeling \& Animation \\
Statistical Reasoning \\
Media, Culture, \& Society \\
Cultural Psychology \\
Marketing Management
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\descript{Programming}
\location{Languages:}
Ruby \textbullet{} Elixir \textbullet{} JS \textbullet{} HTML/CSS \textbullet{} CSS \\
\location{Frameworks:}
Rails/Sinatra/Grape \textbullet{} Elixir \textbullet{} React/React Native \textbullet{} Angular \\
\location{Databases:}
PostgreSQL \textbullet{} Firebase \textbullet{} Redis \\
\descript{Design}
\location{Adobe:}
Photoshop \textbullet{} Illustrator \textbullet{} Sketch \\
\location{Prototyping:}
Invision \textbullet{} FramerJS \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/mopineyro}{\custombold{mopineyro}} \\
LinkedIn://  \href{https://www.linkedin.com/in/manuelopineyro}{\custombold{manuelopineyro}} \\
Twitter://  \href{https://twitter.com/mopineyro}{\custombold{@mopineyro}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{SQWAD}
\descript{| Co-founder, Designer, \& Developer }
\location{Dec 2015 - Present | New York, NY}
\textit{Native Mobile App} - several iOS applications for AHL, WHL, WNBA (league and team)
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Manage design and development of team apps with real-time fantasy sports gaming feature.
\item Built native iOS app using RubyMotion, React Native, and Firebase.
\item Backend Ruby Grape API for managing team reward store.
\item Elixir/Phoenix data feed and points allocation API.
\end{tightemize}
\sectionsep

\runsubsection{Pick6}
\descript{| Freelance Mobile App Design \& Development }
\location{Nov 2014 - Dec 2015 | Portland, OR}
\textit{Hybrid Mobile App} - fan engagement iOS application for minor league hockey team
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item UI modifications and style customization using Sass, Bourbon, and Neat.
\item Ember.js front end feature additions, including: online radio streaming capabilities, graphing of user points, and interactive gaming functionality.
\item Fixes on back end Rails API to support authentication and newly added gamification features.
\end{tightemize}
\sectionsep

\runsubsection{Nike}
\descript{| Application Engineer }
\location{Jan 2015 - Oct 2015 | Beaverton, OR}
\textit{Commerce Engines - Consumer Digital Technology} - SMS, email, and customer communications applications frontend/backend engineering.
\begin{tightemize}
\item Helped plan and build communications services for Nike's international e-commerce rollout.
\item Maintained backend support services for massive post-purchase communication systems.
\item Designed and automated internationalization of email campaigns.
\end{tightemize}
\sectionsep

\runsubsection{Bunker}
\descript{| Jr Web Developer }
\location{May 2014 – Dec 2014 | Beaverton, OR}
\textit{Debt Collection App} - internal app for major debt collection agency based in the Pacific Northwest.
\begin{tightemize}
\item Modified Redis and Rails based API to allow for multiple simultaneous payments.
\item JavaScript refactoring, validations, and bug fixing for a number of front end defects.
\end{tightemize}
\textit{UseMusic.org} - platform for digital music purchases where the proceeds go to a cause of the artist’s choice
\begin{tightemize}
\item Design and implementation of infinite scrolling and faceted search capabilities using Angular and Solr.
\item Expanded unit tests using RSPec and Capybara to ensure continued integrity of app.
\end{tightemize}
\sectionsep

\runsubsection{}
\descript{VivaStreet | Marketing Designer }
\location{Aug 2012 – July 2013 | London, UK \& New York, NY}
\sectionsep

\runsubsection{}
\descript{Columbia Center on Global Brand Leadership | Design Intern}
\location{Sep 2011 – June 2012 | New York, NY}
\sectionsep

\runsubsection{}
\descript{Columbia Computer Graphics Group | Assistant}
\location{Sep 2010 – May 2011 | New York, NY}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Interests
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Interests}
\textbullet{} Physical Computing \textbullet{} Interaction Design \textbullet{} Affective Computing \\ \textbullet{} Data Visualization  \textbullet{} Mobile \textbullet{} Computer Vision \textbullet{} Blockchain

\end{minipage} 
\end{document}  \documentclass[]{article}
